IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-18 paper/real.tex

\subsection{Haskell}
\label{sec:real:hs}
Our work borrows ideas from a Haskell coarse-grained IFC
system called LIO~\cite{lio, stefan:addressing-covert}.
%
LIO relies on Haskell's strong type system and monadic encoding of
side-effecting computations to achieve isolation and define the IFC
sub-language.
%
Specifically LIO provides the \verb|LIO| monad as a way of restricting
(almost all) side-effects; this monad also keeps track of a current
label which is, in turn, used by trusted code when defining core IFC
functions, such as |getLabel|.
%
In the context of our framework, LIO can be understood as follows: the
\emph{pure subset} of Haskell is the target language, while the
monadic subset of Haskell, operating in the \verb|LIO| monad, is the
IFC language.

%Indeed, by rephrasing LIO in terms of our framework, we simplified
%LIO's treatment of exceptions.
%
LIO originally associated labels with exceptions, in a
similar style to fine-grained
systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
%
In particular, the label of an exception was set to the current label
at the time of the throw, and used by a custom catch construct to
raise the current label, thereby preventing leaks due to exceptional
control flows.
%
In addition to being overly complex, the interaction of exceptions
with clearance (which sets an upper bound on the current label, see
Section~\ref{sec:clearance}) was incorrect: the clearance
was restored to the clearance at point of the catch (a consequence of
defining \verb|LIO| using a State monad).
%
Furthermore, pure exceptions (e.g., divide by zero) always percolated to
trusted code, effectively allowing for denial of service attacks.
%
The insights gained when viewing coarse-grained IFC as presented in this
paper led to a much cleaner, simpler treatment of exceptions in LIO,
which has now been adapted by LIO.
%By using isolated tasks, and thus treating the current label (and
%clearance) as global, the underlying Haskell exception system can be
%used directly: exceptional control flow does not affect IFC.

>>>>

%\subsection{Haskell}
%\label{sec:real:hs}
%Our work borrows ideas from a Haskell coarse-grained IFC
%system called LIO~\cite{lio, stefan:addressing-covert}.
%%
%LIO relies on Haskell's strong type system and monadic encoding of
%side-effecting computations to achieve isolation and define the IFC
%sub-language.
%%
%Specifically LIO provides the \verb|LIO| monad as a way of restricting
%(almost all) side-effects; this monad also keeps track of a current
%label which is, in turn, used by trusted code when defining core IFC
%functions, such as |getLabel|.
%%
%In the context of our framework, LIO can be understood as follows: the
%\emph{pure subset} of Haskell is the target language, while the
%monadic subset of Haskell, operating in the \verb|LIO| monad, is the
%IFC language.
%
%%Indeed, by rephrasing LIO in terms of our framework, we simplified
%%LIO's treatment of exceptions.
%%
%LIO originally associated labels with exceptions, in a
%similar style to fine-grained
%systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
%%
%In particular, the label of an exception was set to the current label
%at the time of the throw, and used by a custom catch construct to
%raise the current label, thereby preventing leaks due to exceptional
%control flows.
%%
%In addition to being overly complex, the interaction of exceptions
%with clearance (which sets an upper bound on the current label, see
%Section~\ref{sec:clearance}) was incorrect: the clearance
%was restored to the clearance at point of the catch (a consequence of
%defining \verb|LIO| using a State monad).
%%
%Furthermore, pure exceptions (e.g., divide by zero) always percolated to
%trusted code, effectively allowing for denial of service attacks.
%%
%The insights gained when viewing coarse-grained IFC as presented in this
%paper led to a much cleaner, simpler treatment of exceptions in LIO,
%which has now been adapted by LIO.
%%By using isolated tasks, and thus treating the current label (and
%%clearance) as global, the underlying Haskell exception system can be
%%used directly: exceptional control flow does not affect IFC.
